### 2010-06-11 subarchitectures/visualization.sa/trunk/doc/v11n.tex
v11n: docs updated

The server can display various types of objects. Initially it was created to
display images, but with time other objects (supported by Qt) were added:
SVG images and OpenGL scenes.

@@

@@

\subsection{TODO: Transformations}

>>>>

The server can display various types of objects. Initially it was created to
display images, but with time other objects (supported by Qt) were added:
SVG images, HTML documents and OpenGL scenes.

@@

\subsection{HTML documents}

The display server renders HTML documents with Qt-WebKit. It provides the
sturcture of the HTML document while display clients provide chunks of
HTML code that goes into the body of the document.
\todo{TODO: Add support to modify head of document so that CSS can be used}
The client-side interface for defining HTML document chunks is:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   void setHtml(const std::string& id, const std::string& partId,
         const std::string& htmlData); 
\end{Verbatim}

@@
